Generality in food webs scales with species richness, not latitude

### 2015-01-27 manuscript/latitudepaper.tex
to be overwritten

In this data set, the best fit models for species richness and links per species did not include an 
effect of latitude on either the scaling exponent or residual (Table \ref{Bestfits}). 
$G$ increased slightly in more recent webs ($\rho_{2}$=0.005, $p$\textless0.001), but the best-fit models for $V$ and $Z$ did not include a term for year of publication. 
In contrast, $Z$ and $V$ were higher in lake food webs ($\beta_{4}$=0.10, $p$\textless0.001 and $\beta_{4}$=0.10, $p$\textless0.001, respectively) while the best-fit model for $G$ did not include an effect for any ecosystem type.

@@

\begin{center}
\begin{table}[!h]
\caption{Symbols for and descriptions of food-web properties.}
\label{symboltable}
\begin{tabular}{c l l}
\hline
Symbol      & Name & Description \\
\hline
S & Species richness & Number of trophic species \\
LS & Links per species & Mean number of links per taxon \\
C & Connectance & Number of observed links divided by the number of possible links ($L/S^{2}$) \\
\%Top & \% Top predators & Percentage of taxa without consumers \\
\%Int & \% Intermediate consumers & Percentage of taxa with both consumers and resources \\
\%Basal & \% Basal Resources & Percentage of taxa without resources \\
\%Herb	& \% Herbivores	& Percentage of herbivores and detrivores (taxa that feed on basal taxa) \\
\%Omni & \%Omnivores & Percentage of omnivores (taxa that feed on ≥2 taxa with different trophic levels) \\
Gen & Generality & Mean number of resources per taxon \\
GenSD & SD of generality & Standard deviation of resources per taxon \\
Vul & Vulnerability & Mean number of consumers per taxon \\
VulSD & SD of vulnerability & Standard deviation of consumers per taxon \\
LinkSD & SD of links per species & Standard deviation of links (consumers and resources) per taxon \\
SWTL & Mean short-weighted trophic level & Short-weighted trophic level averaged across taxa \\
Path & Path length & Characteristic path length, the mean shortest food chain between species pairs \\
\hline
\end{tabular}
\end{table}
\end{center}
% NODF & Average Nestedness & Degree to which interactions among specialists are subsets or interactions among generalists \\
% Chain & Chain length & Mean food chain length \\
% Cluster & Clustering coefficient & Mean clustering coefficient (probability that two taxa linked to the same taxon are also linked) \\

@@

\section*{Figures}

\begin{figure}[!h]
\label{gen_all}
\includegraphics[width=.9\textwidth]{Figures/gen_all.eps}
\caption{Relationships between mean generality and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
\end{figure}

\begin{figure}[!h]
\label{TL_all}
\includegraphics[width=.9\textwidth]{Figures/TL_all.eps}
\caption{Relationships between mean trophic level and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
\end{figure}

>>>>

In this data set, none of the best fit models for species richness, connectance, or links per species included an 
effect of latitude on either the scaling exponent or residual (Table \ref{Bestfits}). 
$G$ increased slightly in more recent webs ($\rho_{2}$=0.005, $p$\textless0.001), but the best-fit models for $V$ and $Z$ did not include a term for year of publication. 
In contrast, $Z$ and $V$ were higher in lake food webs ($\beta_{4}$=0.10, $p$\textless0.001 and $\beta_{4}$=0.10, $p$\textless0.001, respectively) while the best-fit model for $G$ did not include an effect for any ecosystem type.

@@

\begin{center}
\begin{table}[!h]
\caption{Symbols for and descriptions of food-web properties.}
\label{symboltable}
\begin{tabular}{c l l}
\hline
Symbol      & Name & Description \\
\hline
S & Species richness & Number of trophic species \\
LS & Links per species & Mean number of links per taxon \\
Gen & Generality & Mean number of resources per taxon \\
Vul & Vulnerability & Mean number of consumers per taxon \\
\hline
\end{tabular}
\end{table}
\end{center}
% NODF & Average Nestedness & Degree to which interactions among specialists are subsets or interactions among generalists \\
% Chain & Chain length & Mean food chain length \\
% Cluster & Clustering coefficient & Mean clustering coefficient (probability that two taxa linked to the same taxon are also linked) \\

@@

% \newpage

% \section*{Figures}

% \begin{figure}[!h]
% \label{gen_all}
% \includegraphics[width=.9\textwidth]{Figures/gen_all.eps}
% \caption{Relationships between mean generality and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
% \end{figure}

% \begin{figure}[!h]
% \label{TL_all}
% \includegraphics[width=.9\textwidth]{Figures/TL_all.eps}
% \caption{Relationships between mean trophic level and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
% \end{figure}
